\documentclass{article}
\usepackage[top=50pt,bottom=90pt,left=110pt,right=105pt]{geometry}
\usepackage{color}
\usepackage{amssymb,amsmath,amsfonts,mathtools}
\usepackage{footnote, hyperref}
\usepackage{float}

\newcommand{\trp}{\mathsf{H}}
\newcommand{\marmousi}{\texttt{Marmousi-II} }

\begin{document}

\title{\bf An MSSS-Preconditioned Matrix Equation Approach for the Time-Harmonic Elastic Wave Equation at Multiple Frequencies\footnote{Submission number: COMG-D-16-00141}}
\author{- Authors' Proof -}

\maketitle


\noindent \textbf{Queries:}

\begin{itemize}
 \item[Q1:] The authors M. Baumann, R. Astudillo and M. B. van Gijzen have identical affiliation. Please merge the superscripts 1 and 2 in line 5 to: \textsf{Delft University of Technology, Delft, The Netherlands}. Moreover, please change affiliation \#4 to \textsf{Nanyang Technological University, Singapore}.
 \item[Q2:] The font sizes are acceptable here since in both figures we do not put emphasis on the concrete numbers.
 \item[Q3:] Please change text in parenthesis in line 737 to: ... (in Fig. 14 we exemplify setup and numerical solution at $4$ Hz) 
 \item[Q4:] The appendix section is presented correctly.
 \item[Q5:] Please change to:
 \begin{align*}
A &= \begin{bmatrix}
    D_1^A & U_1V_2^\trp & U_1W_2V_3^\trp & U_1W_2W_3V_4^\trp \\
    0 & D_2^A & U_2V_3^\trp & U_2W_3V_4^\trp  \\
    0 & 0 & D_3^A & U_3V_4^\trp  \\
    0 & 0 & 0 & D_4^A
    \end{bmatrix}, \quad \text{and}
\\
B &= \begin{bmatrix}
    D_1^B & 0 & 0 & 0 \\
    P_2Q_1^\trp & D_2^B & 0 & 0  \\
    P_3R_2Q_1^\trp & P_3Q_2^\trp & D_3^B & 0  \\
    P_4R_3R_2Q_1^\trp & P_4R_3Q_2^\trp & P_4Q_3^\trp & D_4^B
    \end{bmatrix}.
\end{align*}
\end{itemize}

\vspace{0.4cm}

\noindent \textbf{Further corrections:}

\begin{itemize}
 \item[5:] Please change the name of the fourth author to \textsf{E. Y. M. Ang}.
 \item[6:] Please add revised date: 13 April 2017.
 \item[24:] Please change the keyword to: \textsf{Multilevel sequentially semiseparable (MSSS) matrices}
 \item[126 -- 128:] Please add a full stop at the end of Eq. (6) and replace lines 126 -- 128 by: All parameter functions are assumed in $L^1(\Omega)$. More specifically, we interpolate data points using $Q_1$ basis functions.
 \item[Alg. 1:] Please change caption: Preconditioned IDR($s$) for linear matrix equations [4]
 \item[Alg. 1, l.2:] Please remove line break after $(0,1)$
 \item[Alg. 1, l.28:] Replace by: Overwrite $k$-th block of $G, U$ by $G_k, U_k$
 \item[Alg. 1, l.34:] Replace comment: \quad $\vartriangleright$ $\rho_0 = 0.7$ recommended in [40]
 \item[Alg. 2, l. 21:] Please change the comment to: \quad $\vartriangleright$ SSS inversion (App. A) \& matrix-matrix multiplication (App. B)
 \item[446:] Please avoid line break, i.e. $R_s^{ij} = W_s^{ij} \equiv 0$ should be in one line.
 \item[t4.5:] Please round 0.55 s to 0.6 s.
 \item[t4.5:] Please round 0.71 s to 0.7 s.
 \item[t4.6:] Please round 2.91 s to 2.9 s.
 \item[t5.5:] Please round 0.50 s to 0.5 s.
 \item[t5.5:] Please round 0.83 s to 0.8 s.
 \item[t5.6:] Please round 2.91 s to 2.9 s.
 \item[t6.4:] Please round 8.18 s to 8.2 s.
 \item[Table 6:] Please adapt the table accordingly:
 
 \begin{table}[H]
  \centering
  \begin{tabular}{lll}
  \hline
   \# RHSs &MSSS factorization& PIDR($s=4)$ \\
   \hline
   \phantom{0}1&60.2 s&\phantom{00}8.2 s (8 iter.) \\
   \phantom{0}5&60.2 s&\phantom{0}25.0 s (8 iter.)\\ 
   10&60.1 s&\phantom{0}43.5 s (8 iter.) \\
   20&60.3 s&108.3 s (8 iter.) \\ 
   \hline
  \end{tabular}
 \end{table}

 \item[Table 7:] Please do not display timings in computer font (no \texttt{texttt} environment necessary).
\end{itemize}

\vspace{0.4cm}

\noindent \textbf{Optional corrections:}

If the text layout allows, please change the following figure captions (additional explanations have been added):
\begin{itemize}
 \item [\textbf{Fig. 7}] Schematic illustration: The diagonal blocks of $\hat{S}$ in Eq. 22 correspond to a sequence of $n_z$ 2D problems in the $xy-$plane. This algebraic decoupling affects the propagation of information along the $z$-axis and, hence, the quality of the preconditioner in 3D. Note that this effect is much less severe in the presence of damping, cf. [7].
 \item [\textbf{Fig. 12}] Speed of S-waves in $m/s$ (top), and real part of the $z$-component of the displacement vector in frequency-domain at $f=4$ Hz (middle) and $f=6$ Hz (bottom) for the \marmousi model, cf. [21] for a complete parameter set. The source location is indicated by the symbol '$\triangledown$'. In the present setting, the water layer of the \texttt{Marmousi-II} model has been removed, and we place the source term at $L_x/3$. 
\end{itemize}


\vspace{2cm}

\hfill We would like to thank you for your excellent services!

\vspace{0.4cm}

\hfill With kind regards,

\hfill Manuel Baumann

\hfill \texttt{m.m.baumann@tudelft.nl}
\end{document}
